IJAR Bayesian Nonparametrics Special Issue Manuscript

### 2015-09-27 ijar-npb-ms.tex
prior predictive

@@

Alternative to system signature that allows for
straightforward computation of system relaibility $\Rsys(t) = P(\Tsys > t)$
for multiple component types.
It separates the (time-invariant) system structure from the time-dependent failure probabilities of components.

Can be seen as applying the law of total probability by partitioning
according to the number of components of type $k$ functioning at time $t$,
denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) 
\end{align*}

@@

Then, the number of functioning components out of the $m_k$ components of type $k$
is binomial distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.

@@

The $p^k_t$'s could be such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
The only strict constraint is that $p^k_{t_j} \ge p^k_{t_{j+1}}$ must hold (assuming no repair).

However, directly choosing $p^k_t$'s is hard,
and fixing values for all $p^k_t$ would furthermore neglect any inherent uncertainty in the particular choice.  
To account for this uncertainty, one can express knowledge on $p^k_t$'s though a prior distribution.
A convenient and natural choice is $p^k_t \sim \be(\alpha^k_t, \beta^k_t)$.

@@

posterior, posterior predictive for $C^k_t$

***Illustration prior-data conflict?

>>>>

Based on expert assumptions and data for component failure distribution,
we calculate the system reliability function $\Rsys(t) = P(\Tsys > t)$.

@@

Alternative to system signature that allows for
straightforward computation of system reliability
for multiple component types.
It separates the (time-invariant) system structure from the time-dependent failure probabilities of components.

Can be seen as applying the law of total probability by partitioning
according to the number of components of type $k$ functioning at time $t$,
denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
\end{align*}

@@

Then, the number of functioning components out of the $m_k$ components of type $k$
is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.

@@

(maybe not relevant for this manuscript, but would it make sense to take Kaplan-Meier estimates for the $p^k_t$'s,
or the NPI bounds for Kaplan-Meier?)

The $p^k_t$'s can be chosen such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
The only strict constraint is that $p^k_{t_j} \ge p^k_{t_{j+1}}$ must hold (assuming no repair).

However, directly choosing the $p^k_t$'s is hard,
and fixing values for all $p^k_t$ would furthermore neglect any inherent uncertainty in the particular choice.  
To account for this uncertainty, one can express knowledge on $p^k_t$ through a prior distribution.
A convenient and natural choice is $p^k_t \sim \be(\alpha^k_t, \beta^k_t)$, a conjugate prior,
leading to the posterior being again Beta:

Having observed the lifetime data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$,
at any fixed time $t$ this results in the observation from the Binomial model described above,
$s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
The posterior is then $p^k_t \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.

The posterior predictive distribution for the number of components surviving at time $t$
of the $m_k$ components in the system, based on the tifetime data and the prior information,
is then Beta-binomial distributed,
$C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
That is, we have
\begin{align*}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \alpha^k_t + s^k_t, m_k - l_k + \beta^k_t + n_k - s^k_t)}
                                                    {B(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)} \,,
\end{align*}
where $B(\cdot, \cdot)$ is the beta function.

@@

***Illustration prior-data conflict with $\bebin$?
